Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-21 resex.tex
Intermediate step in revision of bibliography. Minor changes in front matter.
Another step in revision of bibliography. Re-introduced references on noise.

\documentclass[%
%preprint,
reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
prstab,
%prstper,
floatfix,
%endfloats,
longbibliography
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{color}
%\usepackage{siunitx}
\usepackage{url}

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\DeclareFontFamily{U}{wncy}{}
\DeclareFontShape{U}{wncy}{m}{n}{<->wncyr10}{}
\DeclareSymbolFont{mcy}{U}{wncy}{m}{n}
\DeclareMathSymbol{\Sh}{\mathord}{mcy}{"58}

@@

@@

\author{Miriam Fitterer}
\author{Giulio Stancari}
\email[Corresponding author: ]{stancari@fnal.gov}
\author{Alexander Valishev}
\affiliation{Fermi National Accelerator Laboratory, Batavia, Illinois, USA}

@@

The random excitation is a powerful and flexible halo-cleaning
pattern, but it is also potentially harmful for the proton beam
core. A random pattern can be employed at full strength or added as a
modulation to a continuous mode of operation (depending on the
parameter $a$ in Eq.~\ref{eq:random}). During the 2017 experiment, we
tested the effects of the random excitation at full strength ($a = 1$)
and compared it with the resonant excitations.

>>>>

\documentclass[
prstab,reprint
%,draft
%,preprint,tightenlines
,linenumbers
,longbibliography
,preprintnumbers
,showpacs
,showkeys
,byrevtex
,amsfonts,amssymb,amsmath
,floatfix
%,endfloats
]{revtex4-1}

\usepackage{bm}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{hyperref}

@@

% symbol for Dirac comb
\DeclareFontFamily{U}{wncy}{}
\DeclareFontShape{U}{wncy}{m}{n}{<->wncyr10}{}
\DeclareSymbolFont{mcy}{U}{wncy}{m}{n}
\DeclareMathSymbol{\Sh}{\mathord}{mcy}{"58}

@@

\author{Miriam Fitterer}
\author{Giulio Stancari}
\email[Corresponding author. E-mail: ]{stancari@fnal.gov}
\author{Alexander Valishev}
\affiliation{Fermi National Accelerator Laboratory, Batavia, Illinois, USA}

@@

The random excitation is a powerful and flexible halo-cleaning
pattern, but it is also potentially harmful for the proton beam
core. The effects of random noise in various machines have been
studied extensively in the past (see, for instance,
Refs.~\cite{noise_lebedev_ssc, noise_alexahin_lhc, noise_2007_ohmi,
  noise_2014_ohmi}).

A random pattern can be employed at full strength or added as a
modulation to a continuous mode of operation (depending on the
parameter $a$ in Eq.~\ref{eq:random}). During the 2017 experiment, we
tested the effects of the random excitation at full strength ($a = 1$)
and compared it with the resonant excitations.
